\clearpage
\Title{Supplemental Movies}
\TODO{i think should be in a separate word file}
\begin{Itemize}
  \item Recording of the entire process of lateral root formation. Corresponds to Figure 1E (main text) \href{http://youtu.be/navcxqh7KCo}{\textcolor{blue}{[LINK]}}.
  % \item Time lapse recording of individual datasets:
  % \begin{Itemize}
  % 	\item Time lapse recording \#120803 \href{http://youtu.be/hvoDhoWLdSI}{\textcolor{blue}{[LINK]}}.
  %   \item Time lapse recording \#121204 \href{http://youtu.be/bXf-gO8T0aQ}{\textcolor{blue}{[LINK]}}.
  %   \item Time lapse recording \#121211 \href{http://youtu.be/ru7-g3KWV9E}{\textcolor{blue}{[LINK]}}.
  %   \item Time lapse recording \#130508 \href{http://youtu.be/GApOwRMWmUU}{\textcolor{blue}{[LINK]}}.
  %   \item Time lapse recording \#130607 \href{http://youtu.be/cFemfGbI5yA}{\textcolor{blue}{[LINK]}}.
  % \end{Itemize}
  \item Virtual lateral roots datasets \href{https://youtu.be/JbXwgQ3P6h4}{\textcolor{blue}{[LINK]}}.
  % \item Synchronisation on the number of cells, radial view \href{http://youtu.be/YZFkpcnyjiY}{\textcolor{blue}{[LINK]}}.
  \item Average growth tensor for 20 steps. Corresponds to Figure 2B (main text) \href{https://youtu.be/t2hpMR6VFIg}{\textcolor{blue}{[LINK]}}.
  \item Layers formation in all datasets:
  \begin{Itemize}
    \item Dataset \#130607 \href{http://youtu.be/cdY3t1iVRF8}{\textcolor{blue}{[LINK]}}.
    \item Dataset \#120803 \href{http://youtu.be/yXki6QpltZo}{\textcolor{blue}{[LINK]}}.
    \item Dataset \#121204 \href{http://youtu.be/Bd_UgUVyzrM}{\textcolor{blue}{[LINK]}}.
    \item Dataset \#121211 \href{http://youtu.be/NOouEVqpGj8}{\textcolor{blue}{[LINK]}}.
    \item Dataset \#130508 \href{http://youtu.be/EajarNlRvtA}{\textcolor{blue}{[LINK]}}.
  \end{Itemize}
  \item \emph{Geometric} model of lateral root formation. Corresponds to Figure 1A (main text) \href{https://youtu.be/1bVEY_ORSfI}{\textcolor{blue}{[LINK]}}.
  \item \emph{Random} model of lateral root formation. Corresponds to Figure 5D (main text) \href{https://youtu.be/So1GQrtu41w}{\textcolor{blue}{[LINK]}}.
  \item \emph{1\textsuperscript{st} random then geometric} model of lateral root formation. Corresponds to Figure 5G (main text)
  \href{https://youtu.be/H6RUvnqBTVA}{\textcolor{blue}{[LINK]}}.
  \item \emph{Basal growth} model of lateral root formation. Corresponds to Figure 5J (main text) \href{https://youtu.be/TZqwYTnmAgg}{\textcolor{blue}{[LINK]}}.
  \item \emph{1\textsuperscript{st} asymmetric then geometric} model of lateral root formation. Corresponds to Figure~\ref{fig:Modelsupp}A \href{https://youtu.be/ypBdyjFyqYw}{\textcolor{blue}{[LINK]}}.
  \item \emph{Random with equal areas} model of lateral root formation. Corresponds to Figure~\ref{fig:Modelsupp}B
  \href{https://youtu.be/gB-Qt0_H1ok}{\textcolor{blue}{[LINK]}}.
  \item Time lapse recording of the \emph{aur1-2 aur2-2} double mutant, dataset \#131203. Corresponds to Figure~\ref{fig:auroraRaw} \href{http://youtu.be/y8b-0J4lPHg}{\textcolor{blue}{[LINK]}}.
  \item Altered cell divisions in the \emph{aur1-2 aur2-2} double mutant. Corresponds to Figure~\ref{fig:aurora} \href{http://youtu.be/kkQZub-puVI}{\textcolor{blue}{[LINK]}}.
  \item Layer formation in the \emph{aur1-2 aur2-2} double mutant \href{http://youtu.be/FH5BJ177TGk}{\textcolor{blue}{[LINK]}}.
  \item Lateral root induction by gravistimulation \href{http://youtu.be/sLvVCbWye-E}{\textcolor{blue}{[LINK]}}.
  \item Sample preparation \href{https://youtu.be/uFdOIjmO9vI}{\textcolor{blue}{[LINK]}}.
\end{Itemize}